{ \sffamily \LARGE Electronic supplementary material}\\{\bf \sffamily \LARGE Evolution of reciprocity with limited payoff memory

### 2023-10-31 paper/si.tex

Using this distribution $\mathbf{v}$, we compute player 1's expected payoff as the weighted average

@@

\begin{enumerate}
\item The learner and the role model have their last respective interaction with each other. This happens with probability $1/(N\!-\!1)$. In that case, there are four possible cases for their joint final payoffs, $(u_\resident,u_\mutant)\!\in\!\mathcal{U}_F\!:=\!\big\{(R,R),\,(S,T),\,(T,S)\,(P,P)\big\}$. These outcomes are distributed according to the distribution $\mathbf{v}(\strategy_\resident,\strategy_\mutant)$ (Eq.~\eqref{Eq:vAverage}).  
\item The learner's last interaction was not with the role model, with probability $(N\!-\!2)/(N\!-\!1)$. In this case, there are four different subcases, depending on whether the resident's last interaction partner was a mutant or a resident, and depending on whether the mutant's last interaction partner was a mutant or a resident. As a result, the resident's last one-shot payoff is distributed according to $\mathbf{v}(\strategy_\resident,\strategy_\mutant)$ or $\mathbf{v}(\strategy_\resident,\strategy_\resident)$; the mutant's last payoff is distributed according to $\mathbf{v}(\strategy_\mutant,\strategy_\mutant)$ or $\mathbf{v}(\strategy_\mutant,\strategy_\resident)$, respectively. 
\end{enumerate}

@@

~\\
{\bf Stochastic stability of cooperation.}
To illustrate this formalism, we again use it to characterize the stability of cooperation.  
There is $k\!=\!1$ mutant with strategy \alld{}. The remaining players use the resident strategy \gtft. 
When two residents interact, it follows by Eq.~\eqref{Eq:vAverage} that the outcome of the final round is distributed according to the distribution
\begin{align*}
\Big(\, v_R(\gtft,\gtft),~ v_S(\gtft,\gtft),~ v_T(\gtft,\gtft),~ v_P(\gtft,\gtft)\, \Big) = (1,0,0,0). 
\end{align*}
Similarly, if the mutant interacts with a resident, the final round's outcome is distributed according to 
\begin{align*}
\Big(\, v_R(\alld,\gtft),~ v_S(\alld,\gtft),~ v_T(\alld,\gtft),~ v_P(\alld,\gtft)\, \Big) = \big(0,~0,~1\!-\!\delta\!+\!\delta q,~\delta(1\! -\! q)\big). 
\end{align*}
Based on these, we compute the probability $x(u_\resident,u_\mutant)$ that the
payoff of a randomly chosen \gtft{} player is~\(u_\resident\) and that the payoff of the
\alld{} player is \(u_\mutant\), with $u_\resident,u_\mutant \!\in\!\mathcal{U}$. We obtain
\begin{equation*}  \setlength{\arraycolsep}{0.5cm}
\begin{array}{ll}
  x(R, T) =  \frac{N - 2}{N - 1} \cdot (1 - \delta + \delta q)
  &x(R, P) =  \frac{N - 2}{N - 1} \cdot \delta (1 - q) \\[0.25cm]
  x(S, T) =  \frac{1}{N - 1} \cdot (1 - \delta + \delta q) 
  &x(P, P) =  \frac{1}{N - 1} \cdot \delta (1 - q) \\[0.25cm]
  \multicolumn{2}{c}{x(u_\resident, u_\mutant) = ~0 \text{ for all other payoff pairs } (u_\resident, u_\mutant).}
  \end{array}
\end{equation*}
Based on these expressions, we calculate the ratio of transition probabilities as
\begin{equation*}
\frac{\lambda^{-}_1}{\lambda^{+}_1} = \frac{ \frac{N - 2}{N - 1}  
\left(\frac{ 1 - \delta + \delta q}{1+e^{ \beta c} } 
 + \frac{ \delta  \left(1 - q \right)}{1+ e^{-  \beta  \left(b - c \right)}} \right)  
 +  \frac{1}{N-1}  \left(\frac{1 - \delta + \delta q}{1 + e^{\beta  \left( b + c \right)}}
  + \frac{ \delta  \left(1 - q \right)}{2} \right)}
  { \frac{N - 2}{N - 1}  
\left( \frac{ 1 - \delta + \delta q}{1 + e^{-\beta c}}
+  \frac{ \delta  (1 - q)}{1 +e^{  \beta (b - c)}} \right) 
+  \frac{1}{N -1} \left(\frac{ 1 - \delta + \delta q}{1 + e^{-  \beta (b + c)}}
+  \frac{ \delta  \left(1 - q \right)}{2} \right)}
\end{equation*}
Cooperation is stochastically stable if $\lambda^-_1/\lambda^+_1\!>\!1$. 
While one can solve this inequality for $q$, the resulting condition is somewhat lengthy.  
To obtain a more interpretable condition, we consider the limit of strong selection \(\beta\! \rightarrow\! \infty\) and
large populations \(N \!\rightarrow \!\infty \). In that case, because $b\!>\!c\!>\!0$, the above ratio simplifies to
\begin{equation} \label{Eq:TransitionRatioSimple}
    \frac{\lambda^{-}_1}{\lambda^{+}_1} = \frac{\delta(1 - q)}{1 - \delta + \delta q}.
\end{equation}
This ratio exceeds one if  \(q <1 \!-\! 1/(2 \delta)\). 
For such a strategy to be feasible we require $q\!>\!0$, which in turn implies $\delta\!>\!1/2$. 
Moreover, in the special case that games are infinitely repeated, \(\delta\! \rightarrow\! 1\), we conclude that cooperation is stochastically stable if  \(q \!<\! 1/2\). 
(For \(q\! =\! 1/2\), the payoff of the ALLD player is
\(T \!>\! R\) for half of the time, and it is \(P\! < \! R\) for the other half. The
probability that the number of mutants increase by one equals the probability
that the mutant goes extinct).

@@

{\bf Motivation.} 
In the limited-memory setting, individuals take into account the outcome of one round, and of one interaction. 
This setting can be generalized such that an individual
considers \(m\) rounds and of \(n\) interactions. Here we discuss the case that
the update depends on the last round of \(n\) interactions.

At each step of the evolutionary process, we consider the role model's and the learner's last \(n\) matches. 
We need to define the probability that for each of
the matches they are paired with a mutant, with a resident or with each other.
We assume that each pair is unique, such that the learner and the role model
can be matched at most once. 
The case of \(n\!=\!1\) corresponds to the previous setting of limited memory. 
There we have seen that there are five possible combinations to consider. 
As we increase $n$, the number of possible combinations increases non-linearly; 
for a graphical illustration, see Figure~\ref{fig:matching_tree}. 
In the following, we study the case of \(n=2\), such that the learner takes into account the players' final payoffs of two interactions.\\

@@

\noindent
{\bf Computing the ratio $\lambda^-_k/\lambda^+_k$.}
As before, we assume that either the learner or the role model is a resident, and that the other player involved in the pairwise comparison is a mutant. For $n\!=\!2$, there are 24 possible combinations to consider. 
At the first stage there are five possible combinations. 
These are the same as in the previous setting. 
Either the learner interacts directly with the role model; otherwise we need to take into account whether the resident interacts with a resident or a mutant, and whether the mutant interacts with a resident or a mutant. 
In case the learner and the role model did not directly interact with each other during the first stage, there are again five possible combinations in the second stage. 
Otherwise, if there already was a direct interaction, there are four combinations. 
Hence, there are $4\!\cdot\!5 + 4=24$ combinations in total.

@@

  &&+ \frac{\left(N - k - 2\right) \left(N - k - 1\right)}{(N\!-\!2)(N\!-\!3)} 
  v_{u_{\resident1}}\!(\strategy_\resident,\strategy_\resident) \, v_{u_{\mutant 1}}\!(\strategy_\mutant,\strategy_\resident)  
  \left(\frac{ v_{u_{\resident 2}}\!(\strategy_\resident,\strategy_\mutant)}{N-2} \,1_{(u_{\resident 2},u_{\mutant 2})\in \mathcal{U}_F} + \frac{N-3}{N - 2} [E_1 \!+\! E_2 \!+\! E_3 \!+\! E_4]\right) \biggl]. 
  \end{array}
\end{equation}

@@

   \frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!2}{N\!-\!3} \, v_{u_{\mutant 1}}(\strategy_\resident,\strategy_\resident) \, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident)\right]

@@

 In the seconds stage, they may interact with each other. 

@@

   C_1  = \frac{\left(k - 3\right) \left(k - 1\right)}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant) \, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) \quad
   &C_2 = \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident) \, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) \\[0.5cm] 
   C_3  = \frac{\left(k - 2\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant) \, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident) \quad
   &C_4 = \frac{\left(N - k - 2\right)^{2}}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident) \, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident) 

@@

   D_1  = \frac{\left(k - 2\right)^{2}}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) \quad
   &D_2 = \frac{\left(k - 2\right) \left(N - k - 2\right)}{(N - 3) (N - 4)}\,  v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) \\[0.5cm] 
   D_3  = \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant) \,v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident) \quad
   &D_4 = \frac{\left(N - k - 3\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident) \,v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident) 

@@

   E_1  = \frac{(k - 2)(k - 1)}{(N-3)(N-4)}\, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) \quad
   &E_2 = \frac{\left(k - 1\right) \left(N - k - 2\right)}{(N - 3) (N - 4)}\, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) \\[0.5cm] 
   E_3  = \frac{\left(k - 1\right) \left(N - k - 2\right)}{(N - 3) (N - 4)}\, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident) \quad
   &E_4 = \frac{\left(N - k - 3\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} \,v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident)

@@

  x(RR, TT) =  \frac{N - 3}{N - 1}\left(\delta q - \delta + 1\right)^{2} & 
  x(RR, TP) =  \frac{N - 3}{N - 1} \delta \left(1-q \right) \left(\delta q - \delta + 1\right)\\[0.2cm]
  x(RR, PT) =  \frac{N - 3}{N - 1} \delta \left(1-q\right) \left(\delta q - \delta + 1\right) &
  x(RR, PP) =  \frac{N - 3}{N - 1} \delta^{2}  \left(1 - q\right)^{2}\\[0.2cm]
  x(RS, TT) =  \frac{1}{N-1} \left(\delta q - \delta + 1\right)^{2} &
  x(RS, PT) =  \frac{1}{N-1} \delta \left(1-q\right) \left(\delta q - \delta + 1\right) \\[0.2cm]
  x(RP, TP) =  \frac{1}{N-1} \delta \left(1-q\right) \left(\delta q - \delta + 1\right) &
  x(RP, PP) =  \frac{1}{N-1} \delta^{2} \left(1 - q\right)^{2} \\[0.2cm]
  x(SR, TT) =  \frac{1}{N-1} \left(\delta q - \delta + 1\right)^{2} &
  x(SR, TP) =  \frac{1}{N-1} \delta \left(1-q\right) \left(\delta q - \delta + 1\right)\\[0.2cm]
  x(PR, PT) =  \frac{1}{N-1} \delta \left(1-q\right) \left(\delta q - \delta + 1\right) &
  x(PR, PP) =  \frac{1}{N-1} \delta^{2} \left(1-q\right)^{2}

@@

@@

 \frac{1-(1-\delta(1-q))^2}{(1-\delta(1-q))^2} &\text{if}~ \frac{b}{2} > c \\[0.2cm]
  \frac{\delta(1-q)}{1-\delta(1-q)}  &\text{if}~ \frac{b}{2} = c \\[0.2cm]
  \frac{\delta^2(1-q)^2}{1-\delta^2(1-q)^2} &\text{if}~\frac{b}{2} < c

@@

  q <\frac{\delta - 1 + \sqrt{2}/2}{\delta}	&\text{if}~ \frac{b}{2} > c \\[0.15cm]
  q<1-\frac{1}{2\delta}	&\text{if}~\frac{b}{2}=c\\[0.15cm]
  q <\frac{\delta - \sqrt{2}/2}{\delta}\ &\text{if}~\frac{b}{2} < c

@@

\noindent
{\bf Computing the distribution of outcomes in the penultimate and in the final round of a game.}
To compute the ratio of transition probabilities, again we need to compute how likely it is that the resident and the mutant received any possible combination of two payoffs during the last two rounds. 
We start by computing the players' payoff distribution in the penultimate round.

@@

\begin{Prop}\label{proposition:penultimate_round} 
Consider a repeated game with continuation probability $\delta$, between two players with reactive strategies $\strategy_1\!=\!(y_1, p_1, q_1$)  and $\strategy_2\!=\!(y_2,p_2,q_2)$. 
Let $\hat{v}_u\!=\!\hat{v}_u(\strategy_1,\strategy_2)$ denote the probability that the first player receives the payoff $u\!\in\!\mathcal{U}$ in the penultimate round of the game, conditional on the event that the game lasts at least two rounds. 
Then this probability  $\hat{v}_u$ is again identical to the player's average probability $v_u$ to receive payoff $u$ across all rounds of the game, as specified by Eq.~\eqref{Eq:vAverage}.
\end{Prop}

\begin{proof}
The proof is analogous to the proof of Proposition~\ref{proposition:last_round}. 
Let $\mathbf{\hat{v}}:=(\hat{v}_R, \hat{v}_S, \hat{v}_T, \hat{v}_P)$, and let $\mathbf{\hat{v}}(\tau)$ denote the conditional distribution given that  the last round of the game happens to be round $\tau\!\in\!\{1,2,\ldots\}$ (note that we refer to the initial round as round zero, so the game is assumed to take at least two rounds). 
Similar to Eq.~\eqref{Eq:vTildeSimple}, we obtain
\begin{equation}
\mathbf{\hat v}(\tau) = \mathbf{v_0}\cdot M^{\tau-1}.
\end{equation}
The probability that $\tau\!\ge\!1$ is the last round, conditional on the event that the game takes at least two rounds, is 
$$ \mathbb{P}(\tau ~\text{is final round}~|~\text{there are at least two rounds}\,) = \frac{\delta^\tau(1\!-\!\delta)}{\delta} =  \delta^{\tau-1}(1\!-\!\delta).$$
By the law of total probability, we again obtain $\mathbf{\hat{v}}$ by summing up over all possible last rounds,
\begin{equation}
\hat{v} = \sum_{\tau=1}^\infty \delta^{\tau-1}(1\!-\!\delta)  \cdot \mathbf{v_0}M^{\tau-1} 
=  (1\!-\!\delta)\mathbf{v_0} \sum_{t=0}^\infty \delta^t  M^t. 
\end{equation}
This expression for $\mathbf{\hat{v}}$ coincides with the expression for $\mathbf{v}$ in Eq.~\eqref{Eq:vDefinition}.
\end{proof}

>>>>

Using this distribution $\mathbf{v}$, we compute the first player's expected payoff as the weighted average

@@

\begin{enumerate}
\item The learner and the role model have their last respective interaction with each other. This happens with probability $1/(N\!-\!1)$. In that case, there are four possible cases for their joint final payoffs, $(u_\resident,u_\mutant)\!\in\!\mathcal{U}_F\!:=\!\big\{(R,R),\,(S,T),\,(T,S),\,(P,P)\big\}$. These outcomes follow the distribution $\mathbf{v}(\strategy_\resident,\strategy_\mutant)$ (Eq.~\eqref{Eq:vAverage}).  
\item The learner's last interaction was not with the role model, with probability $(N\!-\!2)/(N\!-\!1)$. In this case, there are four different subcases, depending on whether the resident's last interaction partner was a mutant or a resident, and depending on whether the mutant's last interaction partner was a mutant or a resident. As a result, the resident's last one-shot payoff is distributed according to $\mathbf{v}(\strategy_\resident,\strategy_\mutant)$ or $\mathbf{v}(\strategy_\resident,\strategy_\resident)$; the mutant's last payoff is distributed according to $\mathbf{v}(\strategy_\mutant,\strategy_\mutant)$ or $\mathbf{v}(\strategy_\mutant,\strategy_\resident)$, respectively. 
\end{enumerate}

@@

~\\
{\bf Stochastic stability of cooperation.}
To illustrate this formalism, we again use it to characterize the stability of cooperation.  
There is $k\!=\!1$ mutant with strategy \alld{}. The remaining players use the resident strategy \gtft. 
When two residents interact, it follows by Eq.~\eqref{Eq:vAverage} that the outcome of the final round is distributed according to the distribution
\begin{align*}
\Big(\, v_R(\gtft,\gtft),~ v_S(\gtft,\gtft),~ v_T(\gtft,\gtft),~ v_P(\gtft,\gtft)\, \Big) = (1,0,0,0). 
\end{align*}
Similarly, if the mutant interacts with a resident, the final round's outcome is distributed according to 
\begin{align*}
\Big(\, v_R(\alld,\gtft),~ v_S(\alld,\gtft),~ v_T(\alld,\gtft),~ v_P(\alld,\gtft)\, \Big) = \big(0,~0,~1\!-\!\delta\!+\!\delta q,~\delta(1\! -\! q)\big). 
\end{align*}
Based on these, we compute the probability $x(u_\resident,u_\mutant)$ that the
payoff of a randomly chosen \gtft{} player is~\(u_\resident\) and that the payoff of the
\alld{} player is \(u_\mutant\), with $u_\resident,u_\mutant \!\in\!\mathcal{U}$. We obtain
\begin{equation*}  \setlength{\arraycolsep}{0.5cm}
\begin{array}{ll}
  x(R, T) =  \frac{N - 2}{N - 1} \cdot (1 - \delta + \delta q)
  &x(R, P) =  \frac{N - 2}{N - 1} \cdot \delta (1 - q) \\[0.25cm]
  x(S, T) =  \frac{1}{N - 1} \cdot (1 - \delta + \delta q) 
  &x(P, P) =  \frac{1}{N - 1} \cdot \delta (1 - q) \\[0.25cm]
  \multicolumn{2}{c}{x(u_\resident, u_\mutant) = ~0 \text{ for all other payoff pairs } (u_\resident, u_\mutant).}
  \end{array}
\end{equation*}
Based on these expressions, we calculate the ratio of transition probabilities as
\begin{equation*}
\frac{\lambda^{-}_1}{\lambda^{+}_1} = \frac{ \frac{N - 2}{N - 1}  
\left(\frac{ 1 - \delta + \delta q}{1+e^{ \beta c} } 
 + \frac{ \delta  \left(1 - q \right)}{1+ e^{-  \beta  \left(b - c \right)}} \right)  
 +  \frac{1}{N-1}  \left(\frac{1 - \delta + \delta q}{1 + e^{\beta  \left( b + c \right)}}
  + \frac{ \delta  \left(1 - q \right)}{2} \right)}
  { \frac{N - 2}{N - 1}  
\left( \frac{ 1 - \delta + \delta q}{1 + e^{-\beta c}}
+  \frac{ \delta  (1 - q)}{1 +e^{  \beta (b - c)}} \right) 
+  \frac{1}{N -1} \left(\frac{ 1 - \delta + \delta q}{1 + e^{-  \beta (b + c)}}
+  \frac{ \delta  \left(1 - q \right)}{2} \right)} .
\end{equation*}
Cooperation is stochastically stable if $\lambda^-_1/\lambda^+_1\!>\!1$. 
While one can solve this inequality for $q$, the resulting condition is somewhat lengthy.  
To obtain a more interpretable condition, we consider the limit of strong selection \(\beta\! \rightarrow\! \infty\) and
large populations \(N \!\rightarrow \!\infty \). In that case, because $b\!>\!c\!>\!0$, the above ratio simplifies to
\begin{equation} \label{Eq:TransitionRatioSimple}
    \frac{\lambda^{-}_1}{\lambda^{+}_1} = \frac{\delta(1 - q)}{1 - \delta + \delta q}.
\end{equation}
This ratio exceeds one if  \(q <1 \!-\! 1/(2 \delta)\). 
For such a strategy to be feasible, we require $q\!>\!0$, which in turn implies $\delta\!>\!1/2$. 
Moreover, in the special case that games are infinitely repeated, \(\delta\! \rightarrow\! 1\), we conclude that cooperation is stochastically stable if  \(q \!<\! 1/2\). 
(For \(q\! =\! 1/2\), the payoff of the ALLD player is
\(T \!>\! R\) for half of the time, and it is \(P\! < \! R\) for the other half. The
probability that the number of mutants increase by one equals the probability
that the mutant goes extinct.)

@@

{\bf Motivation.} 
In the limited-memory setting, individuals take into account the outcome of one round, and of one interaction. 
This setting can be generalized such that an individual
considers \(m\) rounds and of \(n\) interactions. Here, we discuss the case that
the update depends on the last round of \(n\) interactions.

At each step of the evolutionary process, we consider the role model's and the learner's last \(n\) matches. 
We need to define the probability that for each of
the matches they are paired with a mutant, with a resident or with each other.
We assume that each pair is unique, such that the learner and the role model
can be matched at most once, which is a reasonable assumption in large populations.
The case of \(n\!=\!1\) corresponds to the previous setting of limited memory. 
There, we have seen that there are five possible combinations to consider. 
As we increase $n$, the number of possible combinations increases non-linearly; 
for a graphical illustration, see Fig.~\ref{fig:matching_tree}. 
In the following, we study the case of \(n=2\), such that the learner takes into account the players' final payoffs of two interactions.\\

@@

\noindent
{\bf Computing the ratio $\lambda^-_k/\lambda^+_k$.}
As before, we assume that either the learner or the role model is a resident, and that the other player involved in the pairwise comparison is a mutant. For $n\!=\!2$, there are 24 possible combinations to consider. 
At the first stage there are five possible combinations. 
These are the same as in the previous setting. 
The learner either interacts directly with the role model or we need to take into account whether the resident interacts with a resident or a mutant, and whether the mutant interacts with a resident or a mutant. 
In case the learner and the role model did not directly interact with each other during the first stage, there are again five possible combinations in the second stage. 
Otherwise, if there already was a direct interaction, there are four combinations. 
Hence, there are $4\!\cdot\!5 + 4=24$ combinations in total.

@@

  &&+ \frac{\left(N - k - 2\right) \left(N - k - 1\right)}{(N\!-\!2)(N\!-\!3)} 
  v_{u_{\resident1}}\!(\strategy_\resident,\strategy_\resident) \, v_{u_{\mutant 1}}\!(\strategy_\mutant,\strategy_\resident)  
  \left(\frac{ v_{u_{\resident 2}}\!(\strategy_\resident,\strategy_\mutant)}{N-2} \,1_{(u_{\resident 2},u_{\mutant 2})\in \mathcal{U}_F} + \frac{N-3}{N - 2} [E_1 \!+\! E_2 \!+\! E_3 \!+\! E_4]\right) \biggl] .
  \end{array}
\end{equation}

@@

   \frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!2}{N\!-\!3} \, v_{u_{\mutant 1}}(\strategy_\resident,\strategy_\resident) \, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident)\right] .

@@

 In the second stage, they may interact with each other. 

@@

   C_1  = \frac{\left(k - 3\right) \left(k - 1\right)}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant) \, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) , \quad
   &C_2 = \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident) \, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) , \\[0.5cm] 
   C_3  = \frac{\left(k - 2\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant) \, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident) , \quad
   &C_4 = \frac{\left(N - k - 2\right)^{2}}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident) \, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident) .

@@

   D_1  = \frac{\left(k - 2\right)^{2}}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) , \quad
   &D_2 = \frac{\left(k - 2\right) \left(N - k - 2\right)}{(N - 3) (N - 4)}\,  v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) , \\[0.5cm] 
   D_3  = \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant) \,v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident) , \quad
   &D_4 = \frac{\left(N - k - 3\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} \, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident) \,v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident) .

@@

   E_1  = \frac{(k - 2)(k - 1)}{(N-3)(N-4)}\, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) , \quad
   &E_2 = \frac{\left(k - 1\right) \left(N - k - 2\right)}{(N - 3) (N - 4)}\, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\mutant) , \\[0.5cm] 
   E_3  = \frac{\left(k - 1\right) \left(N - k - 2\right)}{(N - 3) (N - 4)}\, v_{u_{\resident 2}}(\strategy_\resident,\strategy_\mutant)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident) , \quad
   &E_4 = \frac{\left(N - k - 3\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} \,v_{u_{\resident 2}}(\strategy_\resident,\strategy_\resident)\, v_{u_{\mutant 2}}(\strategy_\mutant,\strategy_\resident) .

@@

  x(RR, TT) =  \frac{N - 3}{N - 1}\left(\delta q - \delta + 1\right)^{2}, & 
  x(RR, TP) =  \frac{N - 3}{N - 1} \delta \left(1-q \right) \left(\delta q - \delta + 1\right) ,\\[0.2cm]
  x(RR, PT) =  \frac{N - 3}{N - 1} \delta \left(1-q\right) \left(\delta q - \delta + 1\right) , &
  x(RR, PP) =  \frac{N - 3}{N - 1} \delta^{2}  \left(1 - q\right)^{2} , \\[0.2cm]
  x(RS, TT) =  \frac{1}{N-1} \left(\delta q - \delta + 1\right)^{2} , &
  x(RS, PT) =  \frac{1}{N-1} \delta \left(1-q\right) \left(\delta q - \delta + 1\right) , \\[0.2cm]
  x(RP, TP) =  \frac{1}{N-1} \delta \left(1-q\right) \left(\delta q - \delta + 1\right) , &
  x(RP, PP) =  \frac{1}{N-1} \delta^{2} \left(1 - q\right)^{2} , \\[0.2cm]
  x(SR, TT) =  \frac{1}{N-1} \left(\delta q - \delta + 1\right)^{2} , &
  x(SR, TP) =  \frac{1}{N-1} \delta \left(1-q\right) \left(\delta q - \delta + 1\right) , \\[0.2cm]
  x(PR, PT) =  \frac{1}{N-1} \delta \left(1-q\right) \left(\delta q - \delta + 1\right) ,  &
  x(PR, PP) =  \frac{1}{N-1} \delta^{2} \left(1-q\right)^{2} .

@@

$} .

@@

 \frac{1-(1-\delta(1-q))^2}{(1-\delta(1-q))^2} &\text{if}~ \frac{b}{2} > c , \\[0.2cm]
  \frac{\delta(1-q)}{1-\delta(1-q)}  &\text{if}~ \frac{b}{2} = c , \\[0.2cm]
  \frac{\delta^2(1-q)^2}{1-\delta^2(1-q)^2} &\text{if}~\frac{b}{2} < c .

@@

  q <\frac{\delta - 1 + \sqrt{2}/2}{\delta}	&\text{if}~ \frac{b}{2} > c , \\[0.15cm]
  q<1-\frac{1}{2\delta}	&\text{if}~\frac{b}{2}=c , \\[0.15cm]
  q <\frac{\delta - \sqrt{2}/2}{\delta}\ &\text{if}~\frac{b}{2} < c .

@@

\noindent
{\bf Computing the distribution of outcomes in the penultimate and in the final round of a game.}
To compute the ratio of transition probabilities, again we need to compute how likely it is that the resident and the mutant received any possible combination of two payoffs during the last two rounds. 
The probability that the game lasts for at least two rounds is $\delta$, since that is the probability of continuing from round zero (the initial round) to round one. The distribution of actions in in the penultimate round, conditioned on there being at least two rounds in the game, is then
\begin{align}
	\frac{1}{\delta} \sum_{t=1}^{\infty} \delta^{t}\left(1-\delta\right) \mathbf{v_{0}} M^{t-1} &= \left(1-\delta\right)\mathbf{v_{0}}\sum_{t=0}^{\infty}\delta^{t}M^{t} ,
\end{align}
which is identical to the expression for $\mathbf{v}$ in Eq.~\eqref{Eq:vDefinition}.
Thus, the probability that the first player receives the payoff $u\!\in\!\mathcal{U}$ in the penultimate round of the game, conditional on the event that the game lasts at least two rounds, is again identical to the player's average probability $v_u$ to receive payoff $u$ across all rounds of the game, as specified by Eq.~\eqref{Eq:vAverage}.

@@

~\\
\noindent
We can now derive a probability distribution for the first player's payoff in the last two rounds of a repeated game. 
To this end, consider the $4\times4$ transition matrix $M(\strategy_1,\strategy_2)=(m_{u,u'})$ according to~Eq.~\eqref{eq:transition_matrix}. 
Instead of the usual indexing of the four rows by numbers, $i\!\in\!\{1,2,3,4\}$, here we label the four rows of this matrix by the first player's payoffs in the previous round, $u\!\in\!\{R,S,T,P\}$. 
Similarly, we label the four columns of this matrix by the resulting payoffs to player~1 in the next round. 
For example, $m_{ST}$ corresponds to the second row and third column of matrix $M$. 
So by Eq.~\eqref{eq:transition_matrix}, $m_{ST} = \bar{q}_1 p_2=(1\!-\!q_1)p_2$.
Based on this notation, we can describe the probability $w_{uu'}(\strategy_1,\strategy_2)$ that player~1 obtains a payoff of $u$ in the penultimate round (probability $v_{u}$) and a payoff of $u'$ in the last round (probability $m_{u,u'}$), giving $w_{uu'}(\strategy_1,\strategy_2) = v_u \cdot m_{u,u'}$.
